Template for GTEx example on cluster

### 2017-10-05 analysis/GTEXzscoreTemplate.Rmd
Files commited by wflow_commit.

```{r}
sfares = readRDS("../data/GTExdata/SFAres/sfaGTExzscore.rds")
par(mfrow = c(2,3),mar=c(5.1,4.1,4.1,2.1)-1.9)
for(k in 1:30){
  barplot(sfares$F[,k],main = paste("factor",k))
}

@@

>>>>

```{r}
sfares = readRDS("../data/GTExdata/SFAres/sfaGTExzscore.rds")
par(mfrow = c(2,3),mar=c(5.1,4.1,4.1,2.1)-1.9)
for(k in 1:30){
  barplot(sfares$F[k,],main = paste("factor",k))
}

@@

### SFA K=3

```{r}
g3 = readRDS('../data/GTExdata/SFAres/sfaK_3.rds')
par(mfrow = c(1,3),mar=c(5.1,4.1,4.1,2.1)-1.9)
for(k in 1:3){
  barplot(g3$F[k,],main = paste("factor",k))
}
```

### plot SFAmix result

```{r}
sfamixres = readRDS("../data/GTExdata/SFAres/sfamixGTExzscore.rds")
dim(sfamixres$L)
dim(sfamixres$F)
```

this is only a rank one matrix. I tried two time. two runs give rank one matrix.
